%Feb 5, 2014
%Draft outline: MSIP
%Chris Carilli
\documentclass[preprint]{aastex}

\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{mdwlist}
\usepackage{natbib}
\usepackage{natbibspacing}
\usepackage{caption}
\usepackage{subcaption}
\setlength{\bibspacing}{0pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\setlength{\headsep}{0pt}
\setlength{\topskip}{0pt}
\setlength{\topmargin}{0pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\setlength{\footnotesep}{8pt}
\pagestyle{empty}
\citestyle{aa}

\newcommand{\compress}{\vspace{-0.12in}}


\def\kperp{k_{\bot}}
\def\kpar{k_{\|}}

%project description 20 pages total

\begin{document}

\title{Hydrogen Epoch of Reionization Array: Characterizing Cosmic Dawn}

\section{Overview} % 1 page ~ project summary? 

A. We propose HERA: next step in reionization roadmap

B. Fulfill NWNH high-priority goals

C. New understanding/techniques => faster, better, cheaper

D. Brief summary of timeline: science along the way, major results before end-decade

\section{Science} total = 8 pages

\subsection{Introduction}    % 1 page + 1 fig = simulated Tb cube + PS evolution

i.physical concepts: reionization and dark ages

ii. Current knowledge: various constrai	nts, 1st galaxy studies...

iii. Important role of 21cm studies highlighted in NWNH

a. Typical ideal sim results: T_B vs. z 'cube' and corresponding power spectrum evolution (Fig)

b. introduce some of the important parameters/processes explored: when? how?
bubble scale? sources? inside out? [much of this could be left for below?)

c. reemphasize that current knowledge is nil, yet demand is high

d. emphasize unique (only?) probe of dark ages

\subsection{HI reionization and dark ages science} % 4 pages total examples using hera 331, plus a number of figures

i. F(HI) vs. z: HERA vs. other techniques (Fig) -- emphasize constaints in unexplored territory

ii. PS sensitivity at fixed z: 127, 331 (Fig)

iii. Various covariance analyses: constraints on different physical processes (Liu/Pober analysis). but
please -- keep this down to a couple of incisive figures and fiducial models. wall paper doesn't sell very well. 

iv. Imaging large scale structure: simulation (Fig) 
    
a) Imaging as a probe of non-Gaussianity and topology of reionization (Fig from Watkinson & Pritchard)
[Not sure if this belongs here, should discuss: b) Bayesian imaging (Figs from Paul Sutter).  
Perhaps a broader impact on the radio community too?]

v. Approaching Dark ages (z=20 to 30): early Xray heating? other (Fig - Liu models)

vi. 21cm forest: perhaps a paragraph on possibilities of small scale structure, if we can find radio galaxy? (Fig) 

vii. Cross-correlation science: perhaps montage Fig showing HI(Tb), galaxies, dark matter... at given epoch

a. Provide environmental context for ALMA/JWST 1st galaxy studies

b. CMB pol 

c. CO/CII IM: optimistic or wrong timescale?
  
d. note: xcorr further mitigates continuum systematics

\subsection{Where we are right now: PAPER, MWA}  % 2 pages

i. describe arrays, state design driven by new understandings as delineated below (Fig)

ii. Using new techniqes, current best limits  (Fig)

iii. what will happen in next 2 years: hopefully detection, but no more

iv. LOFAR: not sure what to say about lofar. but we could emphasize this is difficult measurement with 
profound astrophysical impact. such a situation demands multiple approaches, since initial 'discovery' is 
likely to be low S/N and strongly affected by systematics. multiple approaches are crucial check/verify. 
moreover, even if LOFAR beats MWA and PAPER to discovery, that will just be the start of reionization 
studies, not the end. HERA II is that next required step. 

iv. HERA II: 'gauranteed' detection, full characterization, dark ages, imaging

v. Move 'analysis' stuff here?


\section{Challenges} % 2 pages

\subsection{Foregrounds}  % 1.5pages

i. relative intensities (Fig: Continuum from MWA)

ii. Details on Delay Spectrum approach

a. key: 3D k-space: show wedge and discuss. chromatic sidelobes with characteristic freq scale 
set by baseline length

b. analysis focuses on line-of-sight PS dimension

c. work in EoR window.  different window levels, depending on effective horizon

d. drives design to redundant array: helps calibration, add spectra coherently

e. dictates geometry of antenna elements and other RF stuff. avoid standing waves of given length. 

f. area: drives sensitivity as used in section 2

g. some words about why compact, hex array 

\subsection{Other Challenges} % 0.5 pages

i. Interference: Karoo RFI plots  FIG 

i. Polarization 

D. Ionosphere: 

i. short baselines and narrowish FoV

ii. direction dependent gains?


\section{HERA design and project} % 8 pages

\subsection{Lessons learned recap} % 0.5 page

reemphasize design dictated by new understanding

\subsection{Project component details}  % 6 pages

i. compact hex grid array

ii. 14m elements + broad band (active) dipole feed

iii. Signal transport: RF to nodes, digitize at nodes. fiber to correlator. 

iv. Digital stuff: emphasize 'solved problem'. Casper work. block diagrams...

C. Post correlator data path

i. local storage

ii. transport to data centers

iii. data centers: access? 

D. Data analysis [Move up?]

i. Calibration 

ii. Continuum and removal

iii. Delay spectrum analysis

iv. Other (related) approaches: Bayes, z-variance,

v. HI imaging

E. Array monitoring/maintenance: daily, weekly health monitoring

F. Aspirations [move to facilities section?]

i. FFT correlator

ii. other

\subsection{Five year Schedule and deliverables} % 0.5 page

i. stages and science

ii. first science within 3 or 4 years

iii. main science results before end of decade


\section{Broader impacts} % 1 page

A. pre and post-doctoral students

B. South Africa connection

i. professional development/exchanges

ii. broader outreach in SA

C. Broader astronomy community

i. Data access: transients, SETI, ionosphere

ii. Cross correlation: CMBpol, CO/CII IM

D. Casper open source: good example to build from


\section{VI. Summary: why us and why now?} % 0.5 pages

that's obvious


\clearpage
\setcounter{page}{1}
\thispagestyle{empty}
%\bibliographystyle{apj}
%\bibliographystyle{hapj}
\bibliographystyle{jponew}
\bibliography{biblio}

\end{document}

